---
title: "Identify single peak with metid"
author:
- name: Xiaotao Shen PhD (https://www.shenxt.info/)
date: "Created on 2020-03-28 and updated on `r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: no
  pdf_document:
    toc: no
vignette: >
  %\VignetteIndexEntry{identify_single_peak}
  %\VignettePackage{metid}
  % \VignetteEngine{knitr::rmarkdown}
  % \usepackage[utf8]{inputenc}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

***

Some times we only want to match one peak. We can use `identify_single_peak()` function to identify single peak.

```{r,eval = TRUE, warning=FALSE, message=FALSE,R.options="",cache=FALSE}
library(metid)
library(tidyverse)
```

# **Peak information**

We need the m/z, rt and MS2 information. MS2 must be a matrix with two columns: `mz` and `intensity`.

```{r,eval = TRUE, warning=FALSE, message=FALSE,R.options="",cache=FALSE}
mz <- 472.3032
rt <- 772.906
ms2 <- data.frame(
  mz = c(81.38455,82.19755,85.02840,86.5934,86.98958,89.48135,90.70250,
         93.03886, 102.09140, 103.03903, 116.01658, 127.98412, 
         134.06819, 152.46967, 162.02180, 162.05521, 162.11261),
  intensity = c(1396.341,1488.730,15473.604, 1740.842,2158.014,1351.686,
                1547.099,1325.864,22441.047,76217.016,17809.395,
                1439.743, 1729.786, 1543.765, 2228.743, 
                3508.225, 529120.000),
  stringsAsFactors = FALSE
)
ms2 %>% head()
```

# **Run `identify_single_peak()` function**

## **Load database**

First we load the database from `metid` package and then put them in a `example` folder.

```{r,eval = TRUE,warning=FALSE, message=FALSE,R.options="",cache=FALSE}
##create a folder named as example
path <- file.path(".", "example")
dir.create(path = path, showWarnings = FALSE)

##get database from metid
data("snyder_database_rplc0.0.3", package = "metid")
save(snyder_database_rplc0.0.3, file = file.path(path, "snyder_database_rplc0.0.3"))
```

Now in your `./example`, there are one file, namely `snyder_database_rplc0.0.3`.

```{r,eval = TRUE,warning=FALSE, message=FALSE,R.options="",cache=FALSE}
annotation_result <- 
  identify_single_peak(ms1.mz = mz, 
                       ms1.rt = rt, 
                       ms2 = ms2, 
                       ms1.match.ppm = 15, 
                       rt.match.tol = 30,
                       ms2.match.tol = 0.5, 
                       database = "snyder_database_rplc0.0.3",
                       path = path)
```

`annotation_result` is a `metIdentifyClass` object, so you can use all the functions for it to process.

# **Session information**

```{r,eval=TRUE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
sessionInfo()
```

