---
title: "Output metid database to mgf/msp for other tools"
author:
- name: Xiaotao Shen (https://www.shenxt.info/)
date: "Created on 2020-07-02 and updated on `r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: no
  pdf_document:
    toc: no
vignette: >
  %\VignetteIndexEntry{output_database}
  %\VignettePackage{metid}
  % \VignetteEngine{knitr::rmarkdown}
  % \usepackage[utf8]{inputenc}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  out.width = "100%"
)
```

[`MassBank`](https://massbank.eu/), [`MoNA`](https://mona.fiehnlab.ucdavis.edu/) and some other public databases provide `msp` format database of metabolites. So you can use the functions in `metid` to output `metid` format database to `msp` format which can be used for `GNPS`, `MassBank` and `MoNA`.

# **MassBank**

## `msp` format

Just use the `write_msp_massbank()` function to output `metid` database to `msp` format for MassBank.

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
library(metid)
```

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
write_msp_massbank(databasae = databasae, path = ".")
```

The arguments of `write_msp_massbank()` can be found here `write_msp_massbank()`.


## `mgf` format

Just use the `write_mgf_massbank()` function to output `metid` database to `mgf` format for MassBank.

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
library(metid)
```

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
write_mgf_massbank(databasae = databasae, path = ".")
```

The arguments of `write_msp_massbank()` can be found here `write_msp_massbank()`.




# **MoNA**

## `msp` format

Just use the `write_msp_mona()` function to output `metid` database to `msp` format for mona.

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
library(metid)
```

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
write_msp_mona(databasae = databasae, path = ".")
```

The arguments of `write_msp_mona()` can be found here `write_msp_mona()`.


## `mgf` format

Just use the `write_mgf_mona()` function to output `metid` database to `mgf` format for mona.

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
library(metid)
```

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
write_mgf_mona(databasae = databasae, path = ".")
```

The arguments of `write_msp_mona()` can be found here `write_msp_mona()`.


# **GNPS**

## `msp` format

Just use the `write_msp_gnps()` function to output `metid` database to `msp` format for gnps.

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
library(metid)
```

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
write_msp_gnps(databasae = databasae, path = ".")
```

The arguments of `write_msp_gnps()` can be found here `write_msp_gnps()`.


## `mgf` format

Just use the `write_mgf_gnps()` function to output `metid` database to `mgf` format for gnps.

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
library(metid)
```

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
write_mgf_gnps(databasae = databasae, path = ".")
```

The arguments of `write_msp_gnps()` can be found here `write_msp_gnps()`.

# **Session information**

```{r,eval=TRUE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
sessionInfo()
```
