---
title: "Construct public MS2 datbase using metid"
author:
- name: Xiaotao Shen (https://www.shenxt.info/)
date: "Created on 2020-06-10 and updated on `r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: no
  pdf_document:
    toc: no
vignette: >
  %\VignetteIndexEntry{public_database_construction}
  %\VignettePackage{metid}
  % \VignetteEngine{knitr::rmarkdown}
  % \usepackage[utf8]{inputenc}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  out.width = "100%"
)
```

[`MassBank`](https://massbank.eu/), [`MoNA`](https://mona.fiehnlab.ucdavis.edu/) and some other public databases provide `msp` format database of metabolites. So you can use the functions in `metid` to transform them to `metid` format database.

# **MassBank**

Download the `MassBank` msp database from here: [https://massbank.eu/MassBank/](https://massbank.eu/MassBank/). And then put the `msp` data into one folder.

Then set this folder as you work directory in R.

## **Run `construct_massbank_database()` function**

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
library(metid)
```

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
massbank_database <- construct_mona_database(
  file = "MassBank_NIST.msp",
  path = ".",
  version = "0.0.1",
  source = "MoNA",
  link = "https://mona.fiehnlab.ucdavis.edu/",
  creater = "Xiaotao Shen",
  email = "shenxt1990@163.com",
  rt = FALSE,
  threads = 5
)
```

The arguments of `construct_mona_database()` can be found here `construct_mona_database()`.

massbank_database is a `databaseClass` object, you can print it to see its information.

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
save(massbank_database, file = "massbank_database")
```





# **MoNA**

Download the `MoNA` msp database from here: [https://mona.fiehnlab.ucdavis.edu/downloads](https://mona.fiehnlab.ucdavis.edu/downloads). And then put the `msp` data into one folder.

> Note: Only download the database you need, do NOT use the all MS2 spectra databse which is pretty large size.

Then set this folder as you work directory in R.

## **Run `construct_mona_database()` function**

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
library(metid)
```

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
mona_database <- construct_mona_database(
  file = "MoNA-export-LC-MS-MS_Spectra.msp",
  path = ".",
  version = "0.0.1",
  source = "MoNA",
  link = "https://mona.fiehnlab.ucdavis.edu/",
  creater = "Xiaotao Shen",
  email = "shenxt1990@163.com",
  rt = FALSE,
  threads = 5
)
```

The arguments of `construct_mona_database()` can be found here `construct_mona_database()`.

massbank_database is a `databaseClass` object, you can print it to see its information.

```{r,eval = FALSE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
save(mona_database, file = "mona_database")
```

# **Session information**

```{r,eval=TRUE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
sessionInfo()
```
