---
title: "Version 0.9.2"
author:
- name: Xiaotao Shen PhD (https://www.shenxt.info/)
date: "Created on 2021-03-11 and updated on `r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: no
  pdf_document:
    toc: no
vignette: >
  %\VignetteIndexEntry{Version0_9_2}
  %\VignettePackage{metid}
  % \VignetteEngine{knitr::rmarkdown}
  % \usepackage[utf8]{inputenc}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

***

In `version 0.9.2`, I just modified the `database` argument in `identify_metabolites()` and `identify_metabolite_alls` functions. Now you can put the database in the work directory and then give the database name, and you can also directory provide the database (`databaseClass`) to it.

### **Load demo data**

First we load the MS1 peak and database from `metid` package and then put them in a `example` folder.

```{r,eval = TRUE, warning=FALSE, message=FALSE,R.options="",cache=TRUE}
library(metid)
library(tidyverse)
```

```{r,eval = TRUE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
##create a folder named as example
path <- file.path(".", "example")
dir.create(path = path, showWarnings = FALSE)

##get MS1 peak table from metid
ms1_peak <- system.file("ms1_peak", package = "metid")
file.copy(from = file.path(ms1_peak, "ms1.peak.table.csv"), 
          to = path, overwrite = TRUE, recursive = TRUE)

##get database from metid
database <- system.file("ms2_database", package = "metid")

file.copy(from = file.path(database, "msDatabase_rplc0.0.2"), 
          to = path, overwrite = TRUE, recursive = TRUE)
```

Now in your `./example`, there are two files, namely `ms1.peak.table.csv` and `msDatabase_rplc_0.0.2`, respectively.

### **Use database name**

```{r,eval = TRUE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
annotate_result1 <- 
  identify_metabolites(ms1.data = "ms1.peak.table.csv", 
                       ms1.match.ppm = 15, 
                       rt.match.tol = 1000000, 
                       polarity = "positive", 
                       column = "rp", 
                       path = path, 
                       candidate.num = 3,
                       database = "msDatabase_rplc0.0.2", 
                       threads = 5)
```


### **Use databaseClass object**

```{r,eval = TRUE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
load(file.path(path, "msDatabase_rplc0.0.2"))
```

```{r,eval = TRUE,warning=FALSE, message=TRUE,R.options="",cache=TRUE}
msDatabase_rplc0.0.2
```

Then we can directory provide this database to `identify_metabolites()`:

```{r,eval = TRUE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
annotate_result2 <- 
  identify_metabolites(ms1.data = "ms1.peak.table.csv", 
                       ms1.match.ppm = 15, 
                       rt.match.tol = 1000000, 
                       polarity = "positive", 
                       column = "rp", 
                       path = path, 
                       candidate.num = 3,
                       database = msDatabase_rplc0.0.2, 
                       threads = 5)
```

> But what should be noticed is that it have different name for database in the final result:

```{r,eval = TRUE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
annotate_result1@database
```

```{r,eval = TRUE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
annotate_result2@database
```

> It is because that if you give the `databaseClass`, so `identify_metabolites` can know the name of database, if just use the `source` and `version` as the name for database.

```{r,eval = TRUE,warning=FALSE, message=FALSE,R.options="",cache=TRUE}
paste(msDatabase_rplc0.0.2@database.info$Source,
      msDatabase_rplc0.0.2@database.info$Version, 
      sep = "_")

```

# **Session information**

```{r,eval=TRUE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
sessionInfo()
```